\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{changepage}
\usepackage{hyperref}

\usepackage{enumitem,amssymb}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{1pt}{\large\hspace{1pt}\cmark}}%
\hspace{-2.5pt}}

\title{Project Proposal}
\author{Brandon Gutzmann\\Newton Hoac\\Brian Chu\\Benjamin Li\\Jung Yu Chang}

\begin{document}
\maketitle
\tableofcontents
\section{Overview}
\textbf{Game Engine:} Blender Game Engine\\
\textbf{Genre:} 3D Third-person Shooter Survival\\
\textbf{Title:} Narwhals of Good Sleep

\section{Storyline and Objective}
\subsection{Summary}
The player is controlling 2-Ply the penguin. The main objective is to survive and/or protect the flag (2-Ply's egg). If the egg is destroyed, 2-Ply can still survive. However, 2-Ply failed as a parent and gets the ``bad'' ending. If 2-Ply manages to keep the egg safe he gets the ``good'' ending. Enemies come in waves and surround the player. 2-Ply has learned to equip weapons of various sorts to combat them.

\subsection{Plot}
2-Ply the Penguin must defend against the invading narwhal troops from the north pole. Due to the disapearence of the southpole, Gnar the narwhal's hoarde of narwhales are here to remove all the penguins and claim the north pole for themselves. With his hands full, 2-Ply must juggle between surviving the devilish attacks and caring for his egg. Armed with only the garbage litered around the land, 2-Ply must use his ingenuity to craft weapons to fight against the narwhals or get wiped off the sea floor.
\subsection{Setting}
\subsubsection{Map Properties}
\begin{itemize}
\item Underwater theme
\item Circular in shape
\item It will take the player around 1 minute to cross or 30 seconds from the middle to an edge.
\item Four main locations: Beach, Coral Reef, Sunken Ship, and Underwater Vents/Volcano. 
\item Items will spawn randomly around the map but weapons are unique to the region in which they are found.
\end{itemize}

\subsection{Objective}
\textbf{Protect the Flag and/or survive}
\subsubsection{Start}
The game starts with 2-Ply holding his egg at the center of the map. A random weapon will spawn in front of 2-Ply. Other weapons will spawn randomly around the map. 2-Ply will have around 60 seconds to collect weapons and set up the egg in a defensive position. 2-Ply can only hold one thing at a time, so he must juggle between weapons and the egg.

\subsubsection{Waves}
There will be 5 waves: 4 normal waves plus the Boss wave. All waves will have enemies coming in from the edge of the map to attack 2-Ply and his egg. The first wave will only consist of one type of enemy the \textit{Nightmare Narwhal}. The second wave will introduce the \textit{Ranged Narwhal}. The third wave \textit{Speedy Narwhal}. The fourth wave will not introduce any new characters, instead the narwhals will be stronger.\\
\textbf{The Boss Wave}\\
The boss is \textit{Gnar the Narwhal king}. He will float down into the center of the map and will be around 10 times larger than 2-ply. He will have special attacks and a lot of health, but he can't move. The three previous types of narwhals will spawn in while the player is battling Gnar.\\

The player will have one minute to move the egg and gather weapons before the waves of enemies spawn. A predetermined amount of enemies of a set difficulty will spawn per wave. Each wave will last approximately 2-3 minutes. Enemies will attempt to kill the player or egg depending on which is closest and visible. If the player is holding the egg then the enemies will try to attack the player. If the player is damaged while holding the egg they drop it and can't pick it up for 1.5 seconds.\\

After the wave completes, the player will have 1 minute to move to another area and collect new weapons and ammunition before the next wave begins.

\subsection{If 2-Ply dies}
The game is over. There will either be a death animation and/or a cut scene. The game will restart to the beginning.
\subsection{How to win}
The player wins if he/she survives all 5 waves.\\
There are two possible endings.\\
1. 2-Ply and his egg both survive. The ``good'' ending is shown.\\
2. Only 2-Ply survives. The ``bad'' ending is shown.
\subsection{How to lose}
The player loses if 2-ply gets killed.

\subsection{Outsourced Assets}
\begin{itemize}
\item Rocks \url{https://assetstore.unity.com/packages/3d/props/exterior/low-poly-styled-rocks-43486}
\item Ship \url{https://assetstore.unity.com/packages/3d/vehicles/sea/free-ships-104215}
\item Sword
\url{https://assetstore.unity.com/packages/3d/props/weapons/rpg-swords-7056}
\item Sniper
\url{https://assetstore.unity.com/packages/3d/props/guns/ksvk-russian-sniper-rifle-72270}
\item Rifle
\url{https://assetstore.unity.com/packages/3d/props/guns/modern-russian-assault-rifle-46033}
\end{itemize}

\section{Characters}
\subsection{Enemies}
\begin{itemize}
\item Nightmare Narwhal (attacks with his horn)
\item Ranged Narwhal (fires his horn)
\item Speedy Narwhal (moves fast, knocks player back)
\item Gnar the Narwhal King (Boss)
\begin{itemize}
\item Shoots lazers from its horn.
\end{itemize}
\end{itemize}
\subsection{Player}
\begin{itemize}
\item 2-Ply the Penguin
\end{itemize}

\subsection{Items}
\begin{itemize}
\item Penguin egg (The flag)
\item Sweeping melee (sword)
\item Long-ranged gun (Sniper)
\item Medium-ranged gun (Rifle)
\item Close-ranged gun (Shotgun)
\item Explosive (Grenade)
\end{itemize}

\section{Character-Character Interactions}
\begin{itemize}
\item Enemies can attack the player
\item The player can attack enemies
\item Enemies can ``detect'' the player
\item Enemies can attack the flag

\end{itemize}
\section{Character-World Interactions}
\subsection{Items}
Items will spawn randomly in the map.\\
Different weapons will spawn in different regions on the map.\\
When the player drops a weapon or the flag, it will drop a few meters away. This allows the player to ``juggle'' multiple weapons if they want to and raises the skill cap of the game.
\begin{itemize}
\item The player can defend him/herself with the flag. It will provide a knock back affect to enemies and do a little bit of damage.
\item The player can pick up the flag (egg)
\item The player can drop the flag (egg)
\item The player can pick up a weapon
\item The player can drop a weapon
\item The player can collect ammunition

\end{itemize}
\subsection{Movement}
\begin{itemize}
\item The player can aim / Move the camera with the mouse. 
\item The player can walk in 4 directions (wasd)
\item The player can sprint by holding down a key (shift)
\item The player can jump (space) and can't jump again until they touch the ground
\item The player can duck (ctrl)
\item The player can attack (left mouse button)
\item The player can aim down his weapon sights (right mouse button)
\item The enemies can walk
\end{itemize}

\section{Milestones}
\begin{adjustwidth}{2.5em}{0pt}
\begin{itemize}
\item \large \textbf{\textit{What is complete : Type of proof}}
\end{itemize}
\textbf{\large Milestone 1:}
\begin{itemize}
\item \textbf{Final Checklist} : updated project proposal
\item \textbf{Final Proposal} : update project proposal
\item Penguin Model : Picture
\item Penguin Movement Animation : Video
\item Egg Model : Picture
\item Enemy Model (Nightmare Narwhal) : Picture
\item Enemy Movement Animation : Video
\end{itemize}
\textbf{\large Milestone 2:}
\begin{itemize}
\item Player Movement : Video
\item Player Aiming : Video
\item Map (2 locations) : Pictures
\item Item Spawn : Video
\item Item pickup/ drop : Video
\item Enemy Movement : Video
\item Enemy LOS : Video
\end{itemize}
\textbf{\large Milestone 3:}
\begin{itemize}
\item Map (2 locations) : Pictures
\item Fire weapons : Video
\item Enemy Spawn : Video
\item Enemy Attack : Video
\item Damage : video
\item Item pick up animation : video
\item Item drop animation : Video
\item Gnar model : Picture
\end{itemize}
\textbf{\large Milestone 4:}
\begin{itemize}
\item Gnar animation : Video
\item Gnar attacks : Video
\item Game Menu : Picture / Video
\item Game options : Picture
\item Game start / First Wave : video
\item Second Wave : Video
\item Third Wave : video
\end{itemize}
\textbf{\large Milestone 5:}
\begin{itemize}
\item Sound effects : Video
\item Music : Video
\item Fourth Wave : Video
\item Final Wave : Video
\end{itemize}
\end{adjustwidth}
\section{Checklist}
\begin{todolist}
\item notdone
\item[\done] done
\item Penguin Model
\item Egg Model
\item Narwhal Model
\item Map Base
\item Beach Model / Texture
\item Coral Reef Model / Texture
\item Sunken Ship Model
\item Volcano Model
\item Underwater Vent Model
\item Weapon Models
\item Player Movement
\item Player Item pick Up
\item Player spawn
\item Player respawn
\item Enemy Spawn animation
\item Wave Start
\item Wave End
\item Wave 1 Design
\item Wave 2 Design
\item Wave 3 Design
\item Wave 4 Design
\item Enemy LOS
\item Enemy Targeting
\item Health Items
\item Weapon upgrades
\item Camera Postioning


\end{todolist}

\end{document}
